---
output: 
  officedown::rdocx_document:
    reference_docx: ../styling/doc_template.docx
    tables:
      style: 'Table'
      layout: autofit
      width: 1.0
      conditional:
       first_row: true
       first_column: false
       last_row: false
       last_column: false
       no_hband: false
       no_vband: true
    # lists:
    #   ol.style: 'Number alignment: Left'
    #   ul.style: List Paragraph
    page_margins:
      bottom: 1
      top: 1
      right: 0.8
      left: 0.8
      header: 0
      footer: 0
      gutter: 0
params:
  is_la_report: false
  school_name: 'Test school academy'
  term: 'Autumn 2024'
  number_invited: 1000
bibliography: ../styling/references.bib
csl: ../styling/the-lancet.csl
nocite: '@*'
execute:
  enabled: true
---

```{r, echo = FALSE, warning = FALSE, message=FALSE}
#| echo: false
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
school_name <- params$school_name
is_la_report <- params$is_la_report
term <- params$term

library(tidyverse)


theme_update(
  panel.grid = element_blank()
)
```


```{r front-page, echo=FALSE, results='asis'}
cat(knitr::knit_child('front-cover.qmd', envir = environment(), quiet = TRUE))
```

\newpage

::: {custom-style="Heading no TOC"}
Contents
:::

`r officer::block_toc(level = 2, style = NULL, separator = ";")`

```{r introduction, echo=FALSE, results='asis'}
cat(knitr::knit_child('introduction.qmd', envir = environment(), quiet = TRUE))
```

\newpage

# School survey results

## School survey response

Pupils in your school completed the survey `r date_range(input_data)`.

Table \@ref(tab:tab-response) shows the response rate.

```{r tab-response, tab.id="tab-response", tab.cap="Response rate", tab.cap.pre="Table"}
tab_responses(input_data, params$number_invited) |> 
  flextable::flextable() |> 
  flextable::delete_part("header") |> 
  flextable::theme_vanilla() |> 
  # flextable::border_inner_h(officer::fp_border("gray", width = 1)) |> 
  flextable::set_table_properties(layout = "autofit", width = 1) |> 
  flextable::set_caption("Response rate", align_with_table = FALSE)
```

## General health

General health is closely related to mental health, with stress and poor
mental wellbeing sometimes causing physical symptoms.

Pupils were asked to rate their own health as either poor/fair/good/excellent.

Figure \@ref(fig:bar-health) shows the percentage of pupils who reported
their health was \'excellent\' or \'good\'.

<!-- compared with the HBSC Scotland national average. Table shows all the responses from pupils. -->

```{r bar-health, fig.cap="% of pupils who report excellent or good health"}

input_data |> 
  bar_by_cat(
    health,
    success = c("Good", "Excellent")
  )

```


\newpage

```{r outtro, echo=FALSE, results='asis'}
cat(knitr::knit_child('outtro.qmd', envir = environment(), quiet = TRUE))
```

\newpage


# References
