---
output: 
  officedown::rdocx_document:
    reference_docx: ../styling/doc_template.docx
    number_sections: true
    tables:
      style: 'Table'
      layout: autofit
      width: 1.0
      conditional:
       first_row: true
       first_column: false
       last_row: false
       last_column: false
       no_hband: false
       no_vband: true
    # lists:
    #   ol.style: 'Number alignment: Left'
    #   ul.style: List Paragraph
    page_margins:
      bottom: 1
      top: 1
      right: 0.8
      left: 0.8
      header: 0
      footer: 0
      gutter: 0
params:
  is_la_report: false
  school_name: 'Test school academy'
  term: 'Autumn 2024'
  number_invited: 1000
  gender_split: true
bibliography: ../styling/references.bib
csl: ../styling/the-lancet.csl
nocite: '@*'
execute:
  enabled: true
---

```{r, echo = FALSE, warning = FALSE, message=FALSE}
#| echo: false
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      fig.height = 4.6,
                      fig.width = 6.3)
school_name <- params$school_name
is_la_report <- params$is_la_report
term <- params$term

library(tidyverse)


theme_update(
  panel.grid = element_blank()
)
```


```{r front-page, echo=FALSE, results='asis'}
cat(knitr::knit_child('front-cover.qmd', envir = environment(), quiet = TRUE))
```

\newpage

::: {custom-style="Heading no TOC"}
Contents
:::

`r officer::block_toc(level = 2, style = NULL, separator = ";")`

```{r introduction, echo=FALSE, results='asis'}
cat(knitr::knit_child('introduction.qmd', envir = environment(), quiet = TRUE))
```

\newpage

# School survey results

## School survey response

Pupils in your school completed the survey `r date_range(input_data)`.

Table \@ref(tab:tab-response) shows the response rate.

```{r tab-response, tab.id="tab-response", tab.cap="Response rate", tab.cap.pre="Table"}
tab_responses(input_data, params$number_invited)
```

## General health

General health is closely related to mental health, with stress and poor
mental wellbeing sometimes causing physical symptoms.

Pupils were asked to rate their own health as either poor/fair/good/excellent.

Figure \@ref(fig:bar-health) shows the percentage of pupils who reported
their health was \'excellent\' or \'good\'.

<!-- compared with the HBSC Scotland national average. Table [tab] shows all the responses from pupils. -->

```{r bar-health, fig.cap="% of pupils who report excellent or good health"}

input_data |> 
  bar_by_cat(
    health,
    success = c("Good", "Excellent")
  )

```

\newpage

## Good Childhood Index: Happiness with various aspects of life

Pupils were asked to rate how happy they are with various aspects of
their life. Response options ranged from 0 to 10, where 0 means \'very
unhappy\', 5 means \'neither happy nor unhappy\' and 10 means \'very
happy\'.

Figure \@ref(fig:bar-lifesat) shows the average score out of 10, for each of
the eleven aspects of life that pupils were asked about.

Figure \@ref(fig:bar-low-lifesat) shows the percentage of pupils who scored low happiness in each
aspect of life. Low happiness is defined as a score of less than 5. For
more information on this index, see page 6.

```{r bar-lifesat, fig.cap="Average scores for different aspects of life", fig.show='hold'}
input_data |> 
  bar_mean_multiple_vars(
    varslist = list(
      lifesat1 = "Overall",
      lifesat2 = "Family",
      lifesat3 = "Home",
      lifesat4 = "Choice",
      lifesat5 = "Friends",
      lifesat6 = "Things you have",
      lifesat7 = "Health",
      lifesat8 = "Appearance",
      lifesat9 = "Future",
      lifesat10 = "School",
      lifesat11 = "Time use"
    )
  )

```

```{r bar-low-lifesat, fig.cap="% of pupils who report low happiness in different aspects of life", fig.show='hold'}
if (params$gender_split) {
  

input_data |>
    bar_multiple_vars(
    varslist = list(
      lifesat1 = "Overall",
      lifesat2 = "Family",
      lifesat3 = "Home",
      lifesat4 = "Choice",
      lifesat5 = "Friends",
      lifesat6 = "Things you have",
      lifesat7 = "Health",
      lifesat8 = "Appearance",
      lifesat9 = "Future",
      lifesat10 = "School",
      lifesat11 = "Time use"
    ),
    success = ~ .x < 5,
    classes = c("P6", "P7"),
    .gender_split = params$gender_split
  )

}
input_data |>
    bar_multiple_vars(
    varslist = list(
      lifesat1 = "Overall",
      lifesat2 = "Family",
      lifesat3 = "Home",
      lifesat4 = "Choice",
      lifesat5 = "Friends",
      lifesat6 = "Things you have",
      lifesat7 = "Health",
      lifesat8 = "Appearance",
      lifesat9 = "Future",
      lifesat10 = "School",
      lifesat11 = "Time use"
    ),
    success = ~ .x < 5,
    classes = "All",
    .gender_split = FALSE
  )
```

\newpage

## WHO-5 Wellbeing Scale

The WHO--5 Wellbeing Index is a five item scale which provides a measure
of emotional functioning. Items are summed to create a score ranging
from 0 to 100. A score of 50 or less on the WHO-5 indicates
low mood (Figure \@ref(fig:bar-wellbeing)).

<!-- The figure also includes the results from the HBSC -->
<!-- Scotland national average. For more information on this scale, see page -->
<!-- 6. -->

```{r bar-wellbeing, fig.cap="% of pupils with low mood"}
input_data |>
  bar_by_cat(who_cat, success = "low")
```

\newpage

## Me and My Feelings

Pupils were asked to complete the Me and My Feelings questionnaire which
measures emotional and behavioural difficulties. The answers to the
sixteen questions are summed to produce scores and pupils classified
into groups according to pre-determined cut-offs: \'as expected\' or
\'elevated\'. Those in the elevated groups may experience difficulties
in this area. For more information on this scale, see page 6.

```{r bar-mm-emotional, fig.cap="Pupils' emotional scores"}
# input_data |> 
#   bar_share_elevated(mm_emotional)
```

```{r bar-mm-behavioural, fig.cap="Pupils' behavioural scores"}
# input_data |> 
#   bar_share_elevated(mm_behavioural)
```

\newpage

## School

### Liking school

Pupils were asked how much they like school at present. Figure \@ref(fig:bar-sch1) shows the
percentage of pupils who like school \'a lot\' or \'a bit\'

<!-- compared with the HBSC Scotland national average. -->

<!-- Table shows all responses to this question for pupils. -->


```{r bar-sch1, fig.cap="% of pupils who like school (a lot or a bit)"}
input_data |> 
  bar_by_cat(
    sch1,
    c("I like it a lot", "I like it a bit")
  )
```

\newpage

### Pressured by schoolwork

Pupils were asked about how pressured they feel about the schoolwork
they have to do. Figure \@ref(fig:bar-sch2) shows the proportion of pupils who feel \'a
lot\' or \'some\' pressure.

<!-- compared with the HBSC Scotland national average. Table shows all responses to this question. -->

```{r bar-sch2, fig.cap="% of pupils who feel a lot of or some pressure from schoolwork"}
input_data |> 
  bar_by_cat(
    sch2,
    c("A lot", "A little")
  )
```

\newpage

### Self-confidence {#self-confidence .col .s12 .lr_zero .black-text}

Pupils were asked \'how often do you feel confident in yourself\'.
Figure \@ref(fig:bar-sch3) shows the proportion of pupils in your who responded they
\'always\' or \'often\' feel confident 
<!-- compared with the HBSC Scotland national average. Table shows all the responses to this question -->
.

```{r bar-sch3, fig.cap="% of pupils who feel always or often confident"}
input_data |> 
  bar_by_cat(
    sch3,
    c("Always", "Often")
  )
```

\newpage

## Social Emotional Health Survey (SEHS)

The Social Emotional Health Survey (SEHS) measures different aspects of
a child\'s social and emotional wellbeing: Gratitude, Zest, Persistence
and Optimism. All these aspects are positive character traits and are
linked to having more positive mental health and greater school
engagement.

The answers in the questionnaire are summed to
create scores out of 16 for gratitude, zest, persistence and optimism.
These four domains are then summed to create an overall covitality
score, out of 64, which is shown in Figure \@ref(fig:bar-coviality).

The SEHS also measures pro-social behaviour which is linked to more positive mental
health. For more information on this scale, see page 6.




```{r bar-sehs, fig.cap="Average score in each SEHS domain"}
input_data |> 
  bar_mean_multiple_vertical(starts_with("sehs"))
```

```{r bar-coviality, fig.cap="Average covitality score"}
input_data |> 
  bar_mean_multiple_vertical(
    starts_with("cov")
  )
```


\newpage

```{r outtro, echo=FALSE, results='asis'}
cat(knitr::knit_child('outtro.qmd', envir = environment(), quiet = TRUE))
```

\newpage


# References
