---
---

## Self-harm

`r sum(!is.na(input_data$selfh1))` pupils were asked if they had ever hurt themselves on purpose.
Results are shown in Figure \@ref(fig:bar-self-harm) for all and then by year groups and gender.

It is difficult to find accurate data on the prevalence of self-harm amongst adolescents, but lifetime self-harm is estimated to be between 10-20% ^58^. A survey of 15-year olds in HBSC England found that 22% of them had reported ever hurting themselves on purpose.


```{r bar-self-harm, fig.cap="% of pupils who have ever hurt themselves on purpose"}
input_data |> 
  share_elevated(
    selfh1,
    levels = c("Prefer not to say", "No", "Yes"),
    .split = FALSE,
    classes, genders
  ) |> 
  censor_summary_data("denom") |> 
  bar_share_elevated()
```


Those pupils who reported that they had ever self-harmed were then asked how often they had done this in the past year (Table \@ref(tab:tab-self-harm)).

Note that this is as a percentage of all those who said they had ever hurt themselves on purpose and is not a percentage of the whole sample.


```{r tab-self-harm, tab.id="tab-self-harm", tab.cap.pre="Table", tab.cap="Frequency of self-harm in past year"}
input_data |>
  filter(selfh1 == "Yes") |> 
  mutate(sh_con = fct_collapse(
    selfh2,
    "1-10 times" = c("6-10 times","2-5 times", "Once"),
    "Don't know or prefer not to say" = c("Don't know", "Prefer not to say")
    )) |> 
  create_full_summary(
    sh_con,
    levels = c("More than 10 times", "1-10 times", "None", "Don't know or prefer not to say"),
    genders,
    classes,
    .gender_split = FALSE
  ) |>
  censor_summary_data("numerator") |>
  table_from_summary()
```

\newpage
