---
---

## Self-harm

[n of pupils] pupils were asked if they had ever hurt themselves on purpose.
Results are shown in Figure 8.1 for alland then by year groups and gender.

It is difficult to find accurate data on the prevalence of self-harm amongst adolescents, but lifetime self-harm is estimated to be between 10-20% ^58^. A survey of 15-year olds in HBSC England found that 22% of them had reported ever hurting themselves on purpose.

<!-- Figure 8.1: % of pupils who have ever hurt themselves on purpose -->

```{r bar-self-harm, fig.cap="% of pupils who have ever hurt themselves on purpose"}
input_data |> 
  share_elevated(
    selfh1,
    levels = c("Prefer not to say", "No", "Yes"),
    .split = FALSE,
    classes, genders
  ) |> 
  censor_summary_data("denom") |> 
  bar_share_elevated()
```


Those pupils who reported that they had ever self-harmed were then asked how often they had done thisin the past year (Table 8.1).
Note that this is as a percentage of all those who said they had ever hurt themselves on purpose and is nota percentage of the whole sample.


```{r tab-self-harm, tab.id="tab-self-harm", tab.cap.pre="Table", tab.cap="Frequency of self-harm in past year"}
input_data |>
  filter(selfh1 == "Yes") |> 
  create_full_summary(
    selfh2,
    levels = c("More than 10 times", "6-10 times", "2-5 times", "Once", "None"),
    genders,
    classes,
    .gender_split = FALSE
  ) |>
  censor_summary_data("numerator") |>
  table_from_summary()
```

